Dark matter halo shape at $z=0$ in the Auriga simulations: radial evolution and alignment with the stellar disk

### 2019-07-19 Document/paper.tex
edit

Observational constraints of the dark matter halo have been in
conflict during the last decade.
Some studies prefer oblate configurations at small
distances around $\leq 20$ kpc
\citep{Law_and_Majewski_2010,Bovy_et_el._2016,Loebman_et_al._2012,Olling_and_Merrifield_2000,Banerjee_and_Chanda_2011} 
while others tend towards more triaxial and prolate configurations on
the outter distances $\geq 20$ kpc
\citep{Vera-Ciro_and_Helmi_2013,Law_and_Majewski_2009,Deg_and_Widrow_2013,Banerjee_and_Chanda_2011}.  
Some other studies are inclined towards prolate configurations even at the inner
parts of the halo \citep{Bowden_et_al._2016}, and
although it previously seemed that a triaxial DM halo on the
outskirts would be necessary to fully explain the characterization
of the Sagittarius stream \citep{Law_and_Majewski_2009}, recent studies
questioned this claim by reporting inconsistencies with narrow stellar
streams \citet{Pearson_et_al._2015} or finding that
the relaxation of other constraints may make this claim unnecessary
\citet{Ibata_et_al._2013} axisymmetrical to ensure the stability of
a hydrodynamical disk embeded in a static DM halo.

@@

The objects in those simulations were selected from a set of 30
isolated halos in the Evolution and Assembly of GaLaxies and their
Environments (EAGLE)  project \citep{Eagle}.   
These halos were randomly selected from a sample of the most isolated
halos at $z=0$ whose virial mass $M_{200}$ was between $10^{12}M_\odot$ and
$2\times 10^{12}M_\odot$. 
The cosmological parameters in these simulatins correspond to
$\Omega_m=0.307$, $\Omega_b=0.048$, $\Omega_\Lambda=0.693$ and a
dimensionless Hubble parameter $h=0.6777$ [CITATION PLANCK 2014]

The selected halos were re-simulated at higher resultion by applying a
zoom-in technique with varying physical realism using the moving-mesh AREPO code
that includes gravity, ideal magnetohydrodynamics (MHD), 
phenomenological descriptions for star formation, chemical enrichment
from supernovae and its stellar feedback.  The simulation also follows
the formation and evolution of black holes together with the Active
Galactic Nuclei feedback \citep{arepo} [CITATIONPAKMORE].

>>>>

Observational constraints of the dark matter halo have been in
conflict during the last decade.
Some studies prefer oblate configurations at small
distances around $\leq 20$ kpc
\citep{LM10,Bovy16,Loebman_et_al._2012,Olling_and_Merrifield_2000,Banerjee_and_Chanda_2011} 
while others tend towards more triaxial and prolate configurations on
the outter distances $\geq 20$ kpc
\citep{Vera-Ciro_and_Helmi_2013,Law_and_Majewski_2009,Banerjee_and_Chanda_2011,Deg_and_Widrow_2013}. 
Some other studies are inclined towards prolate configurations even at the inner
parts of the halo \citep{Bowden_et_al._2016}, and
although it previously seemed that a triaxial DM halo on the
outskirts would be necessary to fully explain the characterization
of the Sagittarius stream \citep{Law_and_Majewski_2009}, recent studies
questioned this claim by reporting inconsistencies with narrow stellar
streams \citet{Pearson_et_al._2015} or finding that
the relaxation of other constraints may make this claim unnecessary
\citet{Ibata_et_al._2013} axisymmetrical to ensure the stability of
a hydrodynamical disk embeded in a static DM halo.

@@

The objects in those simulations were selected from a set of 30
isolated halos in the Evolution and Assembly of GaLaxies and their
Environments (EAGLE)  project \citep{Eagle}.   
These halos were randomly selected from a sample of the most isolated
halos at $z=0$ whose virial mass $M_{200}$ was between $10^{12}M_\odot$ and
$2\times 10^{12}M_\odot$. 
The cosmological parameters in these simulatins correspond to
$\Omega_m=0.307$, $\Omega_b=0.048$, $\Omega_\Lambda=0.693$ and a
dimensionless Hubble parameter $h=0.6777$ \citep{2014A&A...571A..16P}

The selected halos were re-simulated at higher resultion by applying a
zoom-in technique with varying physical realism using the moving-mesh AREPO code
that includes gravity, ideal magnetohydrodynamics (MHD), 
phenomenological descriptions for star formation, chemical enrichment
from supernovae and its stellar feedback.  
The simulation also follows the formation and evolution of black holes
together with the Active Galactic Nuclei feedback
\citep{arepo,2013MNRAS.432..176P}.
